Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-05-18 manuscript.tex
better explaining completeness figure on text

Figure \ref{fig_completeness}b shows the magnitude by time distribution in a scatter plot as well the cumulative number of events which is important to perform the \gls{tcef}. A linear behavior of cumulative rate on the recent years, gives an idea about the constant record trend. For magnitudes greater than 3, this threshold occurs about 1970. For the magnitudes greater than 4 and 5, these limits could be extrapolated to 1950 and 1940, respective and roughly. Figure \ref{fig_completeness}b also show the completeness tables from the \citet{stepp_1972} test and from the literature \citep{assumpcao_et_al_2014}. Tables \ref{tab:completeness_stepp} and \ref{tab:completeness} show each one of these completeness tables.

>>>>

Figure \ref{fig_completeness}b shows the magnitude by time distribution in a scatter plot as well the cumulative number of events which is important to perform the \gls{tcef}. A linear behavior of cumulative rate on the recent years, gives an idea about the constant record trend. For magnitudes greater than 3, this threshold occurs about 1970. For the magnitudes greater than 4 and 5, these limits could be extrapolated to 1950 and 1940, respective and roughly. Figure \ref{fig_completeness}b also show the completeness times and magnitudes computed from the \citet{stepp_1972} procedure and from \citet{assumpcao_et_al_2014}, converting its magnitudes to \gls{sym:MW}. \ref{tab:completeness_stepp} and \ref{tab:completeness} present their values.
